---
title: "Data transformation and conversion"
output:
  word_document: 
    toc: true
    toc_depth: 5
  pdf_document:
    toc: true
    toc_depth: 5
    latex_engine: xelatex
---

## Load packages and the dataset

```{r eval = FALSE}
library(openxlsx)
library(esc)
library(dplyr)
```

There are two well-maintained R packages available for meta-analysis, namely 'metafor' and 'meta'. Here we start with 'metafor' as it provides a detailed example about how to perform meta-analysis for the pre-post study design with continuous variables. As usual, we start with loading the dataset, but we will divide the dataset into two subsets. One for the control group and the other for the experimental group. We further restrict the columns we used in the dataset for simplification.

```{r eval = FALSE}
Dataset <- read.xlsx('~/Documents/Coding/HP407/Dataset_version_latest.xlsx', 'Combined')
Dataset <- Dataset[Dataset$Source != 'excluded', ]
# colnames(Dataset)
```

## Data transformation

### Renaming and adjusting columns

```{r eval = FALSE}

colnames(Dataset)[which(colnames(Dataset)=="Measurement.points.(days.from.start)")] <- 
  "Measurement.point"
Dataset$Measurement.point <- as.numeric(Dataset$Measurement.point)
colnames(Dataset)[which(colnames(Dataset)=="Treatment.duration.(days.from.start)")] <- 
  "Treatment.duration"

colnames(Dataset)[which(colnames(Dataset)=="Baseline.Female.(percent)")] <- 
  "Patient.female_percent"
colnames(Dataset)[which(colnames(Dataset)=="Patient.age.in.year.(mean)")] <- 
  "Patient.mean_age"

colnames(Dataset)[which(colnames(Dataset)=="Baseline.For.studies.in.carers.only:.Caregiver.female.(percent)")] <- 
  "Caregiver.female_percent"
colnames(Dataset)[which(colnames(Dataset)=="Baseline.For.studies.in.carers.only:.Caregiver.age.in.years.(mean)")] <- 
  "Caregiver.mean_age"

Dataset$Country <- 
  relevel(as.factor(Dataset$Country), "Vietnam")
Dataset$Caregiver.intervention.type <- 
  as.factor(Dataset$Caregiver.intervention.type)
Dataset$Caregiver.intervention.type <- 
  relevel(Dataset$Caregiver.intervention.type, 'No intervention')
```

### Combining control and experimental groups

Then, we convert all the data from control and experimental groups of the same study and measurement to the same row with the following code:

```{r}
colnames(Dataset)
```


```{r eval = FALSE}
data_cols <- c("Pre_mean","Recruitment_N","Pre_N","Pre_SD",
               "Post_mean","Post_N","Post_SD",
               "Attrition", "Attrition.percent",
               "Patient.female_percent","Patient.mean_age",
               "Caregiver.female_percent","Caregiver.mean_age")
info_cols <- colnames(Dataset)[-which(colnames(Dataset) %in% data_cols)]
meta_df.ctrl <- 
  Dataset[Dataset$Caregiver.intervention.type == 'No intervention', ]
meta_df.expt <- 
  Dataset[Dataset$Caregiver.intervention.type != 'No intervention',]
meta_df.es <- list()
for (i in 1:nrow(meta_df.expt)){
    item <- meta_df.expt[i, ]
    item_info <- item[info_cols]
    item_data <- item[data_cols]
    colnames(item_data) <- c("Expt_Pre_mean","Expt_Recruitment_N",
                             "Expt_Pre_N","Expt_Pre_SD",
                             "Expt_Post_mean","Expt_Post_N","Expt_Post_SD",
                             "Expt_Artrition", 'Expt_Attrition.percent',
                             "Expt_Patient.female_percent","Expt_Patient.mean_age",
                             "Expt_Caregiver.female_percent","Expt_Caregiver.mean_age")
    
    # selection by study 
    item_data_ctrl <- 
      meta_df.ctrl[meta_df.ctrl$Study.Identifier == item_info$Study.Identifier, ]

    # selection by effect measure
    item_data_ctrl <- 
      item_data_ctrl[item_data_ctrl$Effect.measure	== item_info$Effect.measure, ]
    left.1 <- dim(item_data_ctrl)
    
    # selection by measurement method
    item_data_ctrl <- 
      item_data_ctrl[item_data_ctrl$Measurement.method	== item_info$Measurement.method, ]
    left.2 <- dim(item_data_ctrl)
    
    # selection by measurement type
    item_data_ctrl <- 
      item_data_ctrl[item_data_ctrl$Measurement.type	== item_info$Measurement.type, ]
    left.3 <- dim(item_data_ctrl)
    
    # selection by intervention duration
    item_data_ctrl <- 
      item_data_ctrl[item_data_ctrl$Duration	== item_info$Duration, ]
    left.4 <- dim(item_data_ctrl)
    
    # selection by measurement point
    item_data_ctrl <- 
      item_data_ctrl[item_data_ctrl$Measurement.point	==
                       item_info$Measurement.point, ]
    left.5 <- dim(item_data_ctrl)
    
    # remove duplicates
    item_data_ctrl <- unique(item_data_ctrl)
    left.6 <- dim(item_data_ctrl)
    
    # check whether the selection returns no value
    if (nrow(item_data_ctrl) < 1){
      print(item$Study.Identifier)
      print(item$Effect.measure)
      print(item_data_ctrl)
      print(left.1)
      print(left.2)
      print(left.3)
      print(left.4)
      print(left.5)
      print(left.6)
    }
    
    # check whether the selection is unique
    if (nrow(item_data_ctrl) > 1){
      print(item$Study.Identifier)
      print(item$Effect.measure)
      print(item_data_ctrl)
    }
    
    # subset data from the selection
    item_data_ctrl <- item_data_ctrl[data_cols]
    
    # rename the columns of selected data
    colnames(item_data_ctrl) <- c("Ctrl_Pre_mean", "Ctrl_Recruitment_N",
                                  "Ctrl_Pre_N","Ctrl_Pre_SD",
                                  "Ctrl_Post_mean","Ctrl_Post_N","Ctrl_Post_SD",
                                  "Ctrl_Artrition", 'Ctrl_Attrition.percent',
                                  "Ctrl_Patient.female_percent","Ctrl_Patient.mean_age",
                                  "Ctrl_Caregiver.female_percent","Ctrl_Caregiver.mean_age")
    
    # combine the data into a data entry
    data_item <- cbind(item_info, item_data, item_data_ctrl)
    
    # combine the data entry with previous records
    meta_df.es  <- rbind(meta_df.es , data_item)
    
}
```

When we finish the transformation, we perform multiplicity detection to make sure each measurement is represented by only one data entry, in case of multiple eligible measurement points and scales.

```{r}
meta_df.es
```


### Dealing with multiplicity of measurements

```{r eval = FALSE}
# multiplicity detection
temp_list <- list()
for (effect.measure in unique(meta_df.es$Effect.measure)){
    temp <- meta_df.es[meta_df.es$Effect.measure == effect.measure, ]
    temp_data <- data.frame(table(temp$Study.Identifier))
    temp_list <- c(temp_list, as.character(temp_data[which(temp_data$Freq > 1), ]$Var1))
}
print(unique(temp_list))
```

Thus, we are able to know the listed studies involve multiplicity of measurement. Thus, we need to further adjust the dataset study by study.

```{r eval = FALSE}
# 'Mahdavi 2017' has two intervention groups, so there is no need to change.
# 'Pahlavanzadeh 2010' has two measurement points, we choose 35 days at the end of intervention
meta_df.es <- meta_df.es[- which(meta_df.es$Study.Identifier == 'Pahlavanzadeh 2010' & 
                                   meta_df.es$'Measurement.point' == 65), ]
print(dim(meta_df.es))

# 'Shata 2017' has two measurement points, we choose 56 days at the 
# end of intervention
meta_df.es <- 
  meta_df.es[- which(meta_df.es$Study.Identifier == 'Shata 2017' & 
                       meta_df.es$'Measurement.point' == 146), ]
print(dim(meta_df.es))

# 'Wang 2014a' has two measurement points, we choose 365 days at 
# the end of intervention
meta_df.es <- 
  meta_df.es[- which(meta_df.es$Study.Identifier == 'Wang 2014a' & 
                       meta_df.es$'Measurement.point' == 180), ]
print(dim(meta_df.es))

# 'Zarepour 2020' has two measurement points, we choose 58 days, 
# one month after the end of intervention also the closest measurement point
meta_df.es <- meta_df.es[- which(meta_df.es$Study.Identifier == 'Zarepour 2020' & 
                                   meta_df.es$'Measurement.point' == 118), ]
print(dim(meta_df.es))

# 'Pan 2019' has two measurement points, we choose 150 days,
# one month after the end of intervention also the closest measurement point
meta_df.es <- meta_df.es[- which(meta_df.es$Study.Identifier == 'Pan 2019' & 
                                   meta_df.es$'Measurement.point' == 210), ]
print(dim(meta_df.es))

# 'Guerra 2011' has two measurement scales for caregiver 
# neuropsychiatric symptoms, we choose NPI-Q severity as it is the most 
# comparable to other included studies
meta_df.es <- meta_df.es[- which(meta_df.es$Study.Identifier == 'Guerra 2011' & 
                                   meta_df.es$Measurement.method == 'SRQ-20'), ]
print(dim(meta_df.es))

# 'Orawan 2018' has three measurement points, we choose 56 days, 
# the closest measurement point to the end of intervention
meta_df.es <- meta_df.es[- which(meta_df.es$Study.Identifier == 'Orawan 2018' & 
                                   meta_df.es$'Measurement.point' > 56), ]
print(dim(meta_df.es))

# multiplicity detection again!
temp_list <- list()
for (effect.measure in unique(meta_df.es$Effect.measure)){
    temp <- meta_df.es[meta_df.es$Effect.measure == effect.measure, ]
    temp_data <- data.frame(table(temp$Study.Identifier))
    temp_list <- c(temp_list, as.character(temp_data[which(temp_data$Freq > 1), ]$Var1))
}
unique(temp_list)
```

```{r}
temp_list
meta_df.es[which(meta_df.es$Study.Identifier == "Mahdavi 2017"), ]
```


### Data summarisation

```{r eval = FALSE}
es.stats <- aggregate(meta_df.es[c('Expt_Post_N', 'Ctrl_Post_N')], list(meta_df.es$Effect.measure), FUN=sum, na.rm = TRUE)
es.stats.freq <- data.frame(table(meta_df.es$Effect.measure))
colnames(es.stats)[1] <- 'Effect.measure'
es.stats[es.stats$Effect.measure == "Caregiver burden", ]$Ctrl_Post_N <- 
  es.stats[es.stats$Effect.measure == "Caregiver burden", ]$Ctrl_Post_N - 31
es.stats$Sample_size <- es.stats$Expt_Post_N + es.stats$Ctrl_Post_N
es.stats <- bind_cols(es.stats, 'Freq'=es.stats.freq$Freq)
es.stats <- es.stats[order(- es.stats$Freq), ]
rownames(es.stats) <- NULL
es.stats
```

## Converting summary data

### Subsetting by data type

```{r eval = FALSE}
# es_df <- meta_df.es[meta_df.es$Effect.measure == 'Caregiver burden', ]
meta_df.es.raw <- meta_df.es[meta_df.es$Measurement.type == 'Raw',]
meta_df.es.regression <- meta_df.es[meta_df.es$Measurement.type == 'Regression',]
meta_df.es.smd <- meta_df.es[meta_df.es$Measurement.type == 'SMD',]
meta_df.es.md <- meta_df.es[meta_df.es$Measurement.type == 'MD',]
```

### Converting Cohen's d to Hedge's g

#### Comparing methods

```{r eval = FALSE}
# two different methods to calculate Hedge's g should get the same result
meta_df.es.smd$Expt_Post_mean * (1- (3)/(4*(meta_df.es.smd$Expt_Post_N + meta_df.es.smd$Ctrl_Post_N) - 9))
hedges_g(meta_df.es.smd$Expt_Post_mean, meta_df.es.smd$Expt_Post_N + meta_df.es.smd$Ctrl_Post_N)
```

#### Assigning results

```{r eval = FALSE}
# thus, we assign the values to the effect size columns
meta_df.es.smd$mean.effect <- 
  hedges_g(meta_df.es.smd$Expt_Post_mean, meta_df.es.smd$Expt_Post_N + meta_df.es.smd$Ctrl_Post_N)
meta_df.es.smd$variance <- meta_df.es.smd$Expt_Post_SD^2
meta_df.es.smd$standard_error <- 
  meta_df.es.smd$Expt_Post_SD/sqrt( meta_df.es.smd$Expt_Post_N + meta_df.es.smd$Ctrl_Post_N)
```

### Estimate Hedge's g from beta

#### Estimation with 'esc'

```{r eval = FALSE}
# esc outputs
esc_B(meta_df.es.regression$Expt_Post_mean, 
      meta_df.es.regression$Expt_Post_SD, 
      meta_df.es.regression$Expt_Post_N, 
      meta_df.es.regression$Ctrl_Post_N, 
      es.type = 'd')
```

#### Estimation 1: Coefficient/Variance

```{r eval = FALSE}
# Estimation of ES from beta: Coefficient/Variance
print("Cohen's d:")
meta_df.es.regression$Expt_Post_mean/meta_df.es.regression$Expt_Post_SD
print("Hedge's g:")
meta_df.es.regression$Expt_Post_mean/meta_df.es.regression$Expt_Post_SD * 
  (1- (3)/(4*(meta_df.es.smd$Expt_Post_N + meta_df.es.smd$Ctrl_Post_N) - 9))
```

#### Estimation 2: MD/pooled SD

```{r eval = FALSE}
# Estimation of ES from beta: pooled variance 
# Calculate d according to https://mason.gmu.edu/~dwilsonb/downloads/esformulas.pdf
# But the result is very similar to 'esc' output
s_y <- meta_df.es.regression$Expt_Post_SD
N <- meta_df.es.regression$Expt_Post_N + meta_df.es.regression$Ctrl_Post_N
n1 <- meta_df.es.regression$Ctrl_Post_N
n2 <- meta_df.es.regression$Expt_Post_N
b <- meta_df.es.regression$Expt_Post_mean
print("Cohen's d:")
s_pooled <- sqrt(((s_y^2)*(N-1)-(b^2)*(n1*n2/(n1+n2)))/(N-2))
b/s_pooled
print("Hedge's g:")
(b/s_pooled)* (1- (3)/(4*(meta_df.es.regression$Expt_Post_N + meta_df.es.regression$Ctrl_Post_N) - 9))
```

#### Assigning results

```{r eval = FALSE}
meta_df.es.regression.SMD <- data.frame(esc_B(meta_df.es.regression$Expt_Post_mean, 
                                      meta_df.es.regression$Expt_Post_SD, 
                                      meta_df.es.regression$Expt_Post_N, 
                                      meta_df.es.regression$Ctrl_Post_N, es.type = 'g',
                                      study = meta_df.es.regression$Study.Identifier))
meta_df.es.regression$mean.effect <- meta_df.es.regression.SMD$es
meta_df.es.regression$variance <- meta_df.es.regression.SMD$var
meta_df.es.regression$standard_error <- meta_df.es.regression.SMD$se
meta_df.es.regression
```
### Calculating effect size from mean differences


```{r eval = FALSE}
reserved_cols <- c('Ctrl_Post_mean', 'Ctrl_Post_SD', 'Ctrl_Post_N', 
                   'Expt_Post_mean', 'Expt_Post_SD','Expt_Post_N',
                   'Study.Identifier')

meta_df.es.md.data <- meta_df.es.md[reserved_cols]
meta_df.es.md.data
```
```{r}
row_SMD<- function(row_data){
  transformed <- esc_mean_sd(
    
    grp2m = as.numeric(row_data[1]), 
    grp2sd = as.numeric(row_data[2]), 
    grp2n = as.numeric(row_data[3]), 
    
    grp1m = as.numeric(row_data[4]), 
    grp1sd = as.numeric(row_data[5]), 
    grp1n = as.numeric(row_data[6]), 
    
    es.type = 'g',
    study = row_data[7])

  df <- data.frame(transformed)
  rownames(df) <- NULL
  return(df)
}
meta_df.es.md.SMD <- do.call('rbind', apply(meta_df.es.md.data, 1, row_SMD))
meta_df.es.md.SMD

meta_df.es.md$mean.effect <- meta_df.es.md.SMD$es
meta_df.es.md$variance <- meta_df.es.md.SMD$var
meta_df.es.md$standard_error <- meta_df.es.md.SMD$se
meta_df.es.md
```


### Calculating effect size from raw

#### Using 'escalc' function in metafor

```{r eval = FALSE}
library(metafor)
meta_df.es.transformed <- escalc(m1i=Expt_Post_mean, 
                                 sd1i=Expt_Post_SD, 
                                 n1i=Expt_Post_N, 
                                 m2i=Ctrl_Post_mean, 
                                 sd2i=Ctrl_Post_SD, 
                                 n2i=Ctrl_Post_N,
                                 measure="SMD", 
                                 vtype="UB", 
                                 data=meta_df.es.raw, 
                                 slab = Study.Identifier, 
                                 var.names = c('mean.effect', 'variance'))
#meta_df.es.transformed$mean.effect
#meta_df.es.transformed$variance
```

#### Using 'esc' package

```{r eval = FALSE}
reserved_cols <- c('Ctrl_Pre_mean', 'Ctrl_Pre_SD', 'Ctrl_Post_mean', 'Ctrl_Post_SD',
                   'Ctrl_Post_N', 
                   'Expt_Pre_mean', 'Expt_Pre_SD', 'Expt_Post_mean', 'Expt_Post_SD',
                   'Expt_Post_N',
                   'Study.Identifier')

meta_df.es.raw.data <- meta_df.es.raw[reserved_cols]

row_SMD<- function(row_data){
  transformed <- esc_mean_gain(
    
    pre1mean = as.numeric(row_data[1]), 
    pre1sd = as.numeric(row_data[2]), 
    post1mean = as.numeric(row_data[3]), 
    post1sd = as.numeric(row_data[4]), 
    grp1n = as.numeric(row_data[5]), 
    
    pre2mean = as.numeric(row_data[6]), 
    pre2sd = as.numeric(row_data[7]), 
    post2mean = as.numeric(row_data[8]), 
    post2sd = as.numeric(row_data[9]), 
    grp2n = as.numeric(row_data[10]), 
    
    es.type = 'g',
    study = row_data[11])

  df <- data.frame(transformed)
  rownames(df) <- NULL
  return(df)
}
meta_df.es.raw.SMD <- do.call('rbind', apply(meta_df.es.raw.data, 1, row_SMD))
meta_df.es.raw.SMD
```

```{r eval = FALSE}
meta_df.es.raw$mean.effect <- meta_df.es.raw.SMD$es
meta_df.es.raw$variance <- meta_df.es.raw.SMD$var
meta_df.es.raw$standard_error <- meta_df.es.raw.SMD$se
meta_df.es.raw
```

```{r eval = FALSE}
ncol(meta_df.es.raw)
ncol(meta_df.es.smd)
ncol(meta_df.es.regression)
ncol(meta_df.es.md)
colnames(meta_df.es.smd) <- colnames(meta_df.es.raw)
colnames(meta_df.es.regression) <- colnames(meta_df.es.raw)
colnames(meta_df.es.md) <- colnames(meta_df.es.raw)
#colnames(meta_df.es.raw)
#colnames(meta_df.es.regression)
```

### Combine and save effect size data

```{r eval = FALSE}
meta_df.es.g <- rbind(meta_df.es.raw, 
                      meta_df.es.smd,
                      meta_df.es.regression, 
                      meta_df.es.md)
meta_df.es.g$Recruitment_total_N <- 
  meta_df.es.g$Expt_Recruitment_N + meta_df.es.g$Ctrl_Recruitment_N
meta_df.es.g$Post_total_N <- meta_df.es.g$Expt_Post_N + meta_df.es.g$Ctrl_Post_N

# t(meta_df.es.g[meta_df.es.g$Study.Identifier == 'Mahdavi 2017', ])
meta_df.es.g[meta_df.es.g$Study.Identifier == 'Mahdavi 2017', ]$Post_total_N <- 
  28+30+31
meta_df.es.g[meta_df.es.g$Study.Identifier == 'Mahdavi 2017', ]$Recruitment_total_N <-
  35+32+33

meta_df.es.g$Total_attrition <- 
  meta_df.es.g$Recruitment_total_N - meta_df.es.g$Post_total_N
meta_df.es.g$Total_attrition.percent <- 
  100 * (meta_df.es.g$Total_attrition / meta_df.es.g$Recruitment_total_N) 

meta_df.es.g[meta_df.es.g$Study.Identifier == 'Wang 2012e', ]$Total_attrition.percent <-
  7.7
meta_df.es.g
```

```{r}
library(openxlsx)
write.xlsx(meta_df.es.g, 'Dataset_effect_size_calculated.xlsx')
```

