---
title: "Meta-analysis"
output:
  word_document: 
    toc: true
    toc_depth: 5
  pdf_document:
    toc: true
    toc_depth: 5
    latex_engine: xelatex
---

```{r eval = FALSE}
library(openxlsx)
library(metafor)
library(esc)
library(dmetar)
library(metafor)
library(dplyr)
library(ggpubr)
```

## Meta-analysis with R

```{r}
getSheetNames('Dataset_effect_size_calculated_v1.xlsx')
```
```{r}
meta_df.es.g <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', sheet = 'All')
colnames(meta_df.es.g)
```


### Perform meta-analysis with 'meta'

```{r}
meta_df.es.g <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                          sheet = 'All(Immediate)')
es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
selected_names <- es.freq_df[es.freq_df$Freq > 3, ]$Var1
selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]

library(meta)
m.gen <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = selection_df,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = FALSE,
                 byvar = Effect.measure,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')

pdf('Figures/combined_forest.pdf', width = 8, height = 8.4)
forest(m.gen, 
       overall = FALSE, 
       random = TRUE, 
       fixed = TRUE,
       overall.hetstat = FALSE, 
       study.results = FALSE,
       subgroup.name = NULL,
       test.subgroup = FALSE,
       xlim = c(-5, 5))
dev.off()

pdf('Figures/combined_forest_full.pdf', width = 13, height = 11.5)
forest(m.gen, 
       sortvar = Country,
       overall = FALSE, 
       random = TRUE, 
       fixed = TRUE,
       overall.hetstat = FALSE, 
       prediction.subgroup = TRUE,
       study.results = TRUE,
       subgroup.name = NULL,
       test.subgroup = FALSE,
       leftcols = c('Study.Identifier','Country',
                    'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country', 
                    expression(atop('Intervention','type')),
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       xlim = c(-5, 5))
dev.off()
```

```{r}
es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
selected_names <- es.freq_df[es.freq_df$Freq < 4, ]$Var1
selected_names <- selected_names[grepl('Caregiver', selected_names)]
selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]

library(meta)
m.gen <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = selection_df,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = FALSE,
                 byvar = 'Effect.measure',
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')

pdf('Figures/combined_forest_1.pdf', width = 10, height = 8.4)
forest(m.gen, 
       prediction.subgroup = FALSE, subgroup.name = NULL, 
       overall = FALSE, overall.hetstat = FALSE, 
       leftcols = c('Study.Identifier','Country',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition %',
                    'Overall risk of bias'),
       xlim = c(-5, 5))
dev.off()
```
```{r}
es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
selected_names <- es.freq_df[es.freq_df$Freq < 4, ]$Var1
selected_names <- selected_names[grepl('Patient|Caregiver', selected_names)]
selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]

m.gen <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = selection_df,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = FALSE,
                 byvar = Effect.measure,
                 
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')


pdf('Figures/combined_forest_2.pdf', width = 10, height = 12)
forest(m.gen, 
       prediction.subgroup = FALSE, 
       subgroup.name = NULL, 
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Risk of bias'),
       overall = FALSE, 
       overall.hetstat = FALSE, 
       xlim = c(-5, 5))
dev.off()
```

```{r}
es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
selected_names <- es.freq_df[es.freq_df$Freq >2, ]$Var1
# selected_names <- selected_names[grepl('Caregiver', selected_names)]
selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]

# colnames(caregiver_es)
# caregiver_es_names
caregiver.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = selection_df,
                 sm = "SMD",
                 comb.fixed = TRUE,
                 byvar = Effect.measure)
pdf('Figures/combined_forest_short.pdf', width = 8, height = 6)
forest(caregiver.m, prediction.subgroup = FALSE, 
       subgroup.name = NULL, 
       overall = FALSE, overall.hetstat = FALSE,
       leftcols = NULL, 
       leftlabs = NULL, 
       study.results = FALSE,
       test.subgroup = FALSE,
       xlim = c(-14, 14), print.tau2 = FALSE,
       text.common = 'Fixed-effects model',
       text.random = 'Random-effects model'
       )
dev.off()

pdf('Figures/combined_forest_full.pdf', width = 15, height = 50)
forest(caregiver.m, prediction.subgroup = TRUE, 
       subgroup.name = NULL, 
       overall = TRUE, overall.hetstat = TRUE,
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Risk of bias'),
       study.results = TRUE,
       test.subgroup = TRUE,
       xlim = c(-14, 14), print.tau2 = TRUE,
       text.common = 'Fixed-effects model',
       text.random = 'Random-effects model'
       )
dev.off()
```

### Caregiver burden

#### Perform meta-analysis with 'metafor'

```{r eval = FALSE}
library(metafor)
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
# caregiver_burden
res <- rma(mean.effect, variance, data=caregiver_burden, slab = Study.Identifier)
# res
# forest(res)
library(ggpubr)
ggqqplot(res$data$mean.effect)
shapiro.test(res$data$mean.effect)
```
```{r}
full.model.1 <- rma.mv(yi = mean.effect, 
                     V = variance, 
                     slab = Study.Identifier,
                     data = caregiver_burden,
                     random = ~ 1 |Country/Study.Identifier)
full.model.1
var.comp(full.model.1)
plot(var.comp(full.model.1))

full.model.2 <- rma.mv(yi = mean.effect, 
                     V = variance, 
                     slab = Study.Identifier,
                     data = caregiver_burden,
                     random = ~ 1 |Study.Identifier/Effect.measure)
full.model.2
var.comp(full.model.2)
plot(var.comp(full.model.2))


full.model.2.removed <- rma.mv(yi = mean.effect, 
                     V = variance, 
                     slab = Study.Identifier,
                     data = caregiver_burden,
                     random = ~ 1 | Place.of.intervention.updated/Study.Identifier, 
                     test = "t", 
                     method = "REML",
                     sigma2 =  c(0, NA))

anova(full.model.2, full.model.2.removed)

full.model.3 <- rma.mv(yi = mean.effect, 
                     V = variance, 
                     slab = Study.Identifier,
                     data = caregiver_burden,
                     random = ~ 1 |Caregiver.intervention.type/Study.Identifier)
full.model.3
var.comp(full.model.3)
plot(var.comp(full.model.3))

full.model.3.removed <- rma.mv(yi = mean.effect, 
                     V = variance, 
                     slab = Study.Identifier,
                     data = caregiver_burden,
                     random = ~ 1 | Caregiver.intervention.type/Study.Identifier, 
                     test = "t", 
                     method = "REML",
                     sigma2 =  c(0, NA))

anova(full.model.3, full.model.3.removed)
```

#### Perform GOSH analysis with 'metafor'

```{r eval = FALSE}
qqnorm(res)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
```

#### GOSH after removing outliers

```{r eval = FALSE}
res <- rma(mean.effect, variance, 
           data=caregiver_burden[-5, ], 
           slab = Study.Identifier)
qqnorm(res)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
```

#### Perform meta-analysis with 'meta'
```{r}
colnames(caregiver_burden)
```



```{r}
#es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
#selected_names <- es.freq_df[es.freq_df$Freq < 4, ]$Var1
#selected_names <- selected_names[grepl('Patient', selected_names)]
#selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')

caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 # subgroup = Caregiver.intervention.type,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')

pdf('Figures/caregiver_burden_forest.pdf', width = 12, height = 7)
forest(caregiver_burden.m, 
       prediction = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = NULL, 
       leftcols = c('Study.Identifier','Country',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Country',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition %',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
```
```{r}
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Type.of.funding.source,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.m
pdf('Figures/caregiver_burden_forest(funding).pdf', width = 13, height = 10)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = 'Sponsor', 
       leftcols = c('Study.Identifier','Country', 'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country', 'Type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
subgroup_stats <- data.frame(do.call(cbind, caregiver_burden.m[c('k.w', 
                               'TE.random.w', "lower.random.w", "upper.random.w", 
                               'lower.predict.w','upper.predict.w', 'pval.random.w', 
                               "I2.w", "lower.I2.w", 'upper.I2.w')]))
write.csv(subgroup_stats, "Figures/caregiver_burden_forest(funding).csv")
```
```{r}
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Frequency,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.m
pdf('Figures/caregiver_burden_forest(freq).pdf', width = 13, height = 10)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = NULL, 
       leftcols = c('Study.Identifier','Country', 'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country', 'Type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
subgroup_stats <- data.frame(do.call(cbind, caregiver_burden.m[c('k.w', 
                               'TE.random.w', "lower.random.w", "upper.random.w", 
                               'lower.predict.w','upper.predict.w', 'pval.random.w', 
                               "I2.w", "lower.I2.w", 'upper.I2.w')]))
write.csv(subgroup_stats, "Figures/caregiver_burden_forest(freq).csv")
```


```{r}
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Domain.1,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.m
pdf('Figures/caregiver_burden_forest(domain1).pdf', width = 13, height = 10)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = 'Domain 1', 
       leftcols = c('Study.Identifier','Country', 'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country', 'Type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
subgroup_stats <- data.frame(do.call(cbind, caregiver_burden.m[c('k.w', 
                               'TE.random.w', "lower.random.w", "upper.random.w", 
                               'lower.predict.w','upper.predict.w', 'pval.random.w', 
                               "I2.w", "lower.I2.w", 'upper.I2.w')]))
write.csv(subgroup_stats, "Figures/caregiver_burden_forest(domain1).csv")
```


```{r}
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Domain.2,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.m
pdf('Figures/caregiver_burden_forest(domain2).pdf', width = 13, height = 10)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = 'Domain 2', 
       leftcols = c('Study.Identifier','Country', 'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country', 'Type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
subgroup_stats <- data.frame(do.call(cbind, caregiver_burden.m[c('k.w', 
                               'TE.random.w', "lower.random.w", "upper.random.w", 
                               'lower.predict.w','upper.predict.w', 'pval.random.w', 
                               "I2.w", "lower.I2.w", 'upper.I2.w')]))
write.csv(subgroup_stats, "Figures/caregiver_burden_forest(domain2).csv")
```

```{r}
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Domain.3,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.m
pdf('Figures/caregiver_burden_forest(domain3).pdf', width = 13, height = 10)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = 'Domain 3', 
       leftcols = c('Study.Identifier','Country', 'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country', 'Type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
subgroup_stats <- data.frame(do.call(cbind, caregiver_burden.m[c('k.w', 
                               'TE.random.w', "lower.random.w", "upper.random.w", 
                               'lower.predict.w','upper.predict.w', 'pval.random.w', 
                               "I2.w", "lower.I2.w", 'upper.I2.w')]))
write.csv(subgroup_stats, "Figures/caregiver_burden_forest(domain3).csv")
```

```{r}
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Domain.4,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.m
pdf('Figures/caregiver_burden_forest(domain4).pdf', width = 13, height = 10)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = 'Domain 4', 
       leftcols = c('Study.Identifier','Country', 'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country', 'Type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
subgroup_stats <- data.frame(do.call(cbind, caregiver_burden.m[c('k.w', 
                               'TE.random.w', "lower.random.w", "upper.random.w", 
                               'lower.predict.w','upper.predict.w', 'pval.random.w', 
                               "I2.w", "lower.I2.w", 'upper.I2.w')]))
write.csv(subgroup_stats, "Figures/caregiver_burden_forest(domain4).csv")
```

```{r}
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Domain.2,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.m
pdf('Figures/caregiver_burden_forest(domain5).pdf', width = 13, height = 10)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = 'Domain 5', 
       leftcols = c('Study.Identifier','Country', 'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Country', 'Type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
subgroup_stats <- data.frame(do.call(cbind, caregiver_burden.m[c('k.w', 
                               'TE.random.w', "lower.random.w", "upper.random.w", 
                               'lower.predict.w','upper.predict.w', 'pval.random.w', 
                               "I2.w", "lower.I2.w", 'upper.I2.w')]))
write.csv(subgroup_stats, "Figures/caregiver_burden_forest(domain5).csv")
```


```{r}
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Country,
                 # byvar = Effect.measure,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.m
pdf('Figures/caregiver_burden_forest(country).pdf', width = 13, height = 8)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = Year,
       subgroup.name = NULL, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Study Identifier', 'Intervention type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()

subgroup_stats <- data.frame(do.call(cbind, caregiver_burden.m[c('k.w', 
                               'TE.random.w', "lower.random.w", "upper.random.w", 
                               'lower.predict.w','upper.predict.w', 'pval.random.w', 
                               "I2.w", "lower.I2.w", 'upper.I2.w')]))
write.csv(subgroup_stats, "Figures/caregiver_burden_forest(country).csv")
```


#### Funnel plot

```{r eval = FALSE}
pdf('Figures/caregiver_burden_funnel.pdf', width = 10, height = 7)
# funnel(m.gen, studlab = TRUE, xlim = c(-4, 4))
col.contour = c("gray75", "gray85", "gray95")
funnel.meta(caregiver_burden.m, xlim = c(-4, 1),
            contour = c(0.9, 0.95, 0.99),
            col.contour = col.contour, 
            studlab = TRUE, 
            pos.studlab = '2',
            cex.studlab = 0.7)

# Add a legend
legend(x = -4, y = 0.01, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)
dev.off()

metabias(caregiver_burden.m, method.bias = "linreg")

```
```{r}
caregiver_burden.leave1out <- metainf(caregiver_burden.m)
caregiver_burden.leave1out
write.csv(data.frame(caregiver_burden.leave1out), 'Figures/caregiver_burden_leave1out.csv')
pdf('Figures/caregiver_burden_leave1out.pdf', width = 15, height = 4)
forest(caregiver_burden.leave1out, 
       predict = TRUE,
       prediction.subgroup = FALSE, 
       sortvar = TE,
       subgroup.name = NULL, 
       leftcols = c('Study.Identifier', 'Country',
                    'Caregiver.intervention.type.abbr',
                    'Ctrl_Post_N', 'Expt_Post_N',  
                    'Total_attrition.percent', 
                    'Overall'),
       leftlabs = c('Ignored study', 'Country', 'Intervention type',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Attrition%',
                    'Overall risk of bias'),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-1.8, -0.1))
dev.off()
pdf('Figures/caregiver_burden_infana.pdf', width = 12, height = 6)
inf.analysis <- InfluenceAnalysis(caregiver_burden.m, random = TRUE)
plot(inf.analysis, "I2", return.separate.plots = TRUE)
dev.off()
# plot(caregiver_burden.leave1out,"influence")
find.outliers(caregiver_burden.m)

pdf('Figures/caregiver_burden_pcurve.pdf', width = 8, height = 6)
pcurve(caregiver_burden.m)
dev.off()

forest(subgroup.analysis.mixed.effects(caregiver_burden.m, caregiver_burden.m$subgroup))
```
```{r}
data.frame(caregiver_burden.m)
```

```{r}
library(metafor)
caregiver_burden.mmi <- 
  multimodel.inference(TE = 'mean.effect', 
                       seTE = 'standard_error', 
                       data = caregiver_burden,
                       predictors = c('Year', 
                                      'Total_attrition.percent', 
                                      'Measurement.point',
                                      'Treatment.duration'),
                       method='DL', eval.criterion = 'BIC', interaction = FALSE)
caregiver_burden.mmi
```


#### Subgroup analysis by country

```{r eval = FALSE}
caregiver_burden.m.by.country <- update.meta(caregiver_burden.m, 
            subgroup = Country, 
            tau.common = FALSE)
pdf('Figures/caregiver_burden_country.pdf', width = 10, height = 7.5)
forest(caregiver_burden.m.by.country, 
       subgroup.name = NULL, 
       prediction = TRUE, 
       prediction.subgroup = FALSE,
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")),
       )
dev.off()
caregiver_burden.m.by.country
```

```{r}
caregiver_burden.m.by.country
```

#### Subgroup analysis by intervention type

```{r eval = FALSE}
caregiver_burden.m.by.intervention <- update.meta(caregiver_burden.m, 
            subgroup = Caregiver.intervention.type, tau.common = FALSE)
caregiver_burden.m.by.intervention
pdf('Figures/caregiver_burden_intervention.pdf', width = 10, height = 10)
forest(caregiver_burden.m.by.intervention, subgroup.name = NULL, 
       prediction = TRUE, prediction.subgroup = TRUE)
dev.off()
```

```{r}
caregiver_burden.m.Domain <- update.meta(caregiver_burden.m, 
            subgroup = Domain.1.unmodified, tau.common = FALSE)
caregiver_burden.m.Domain
pdf('Figures/caregiver_burden.m.Domain.pdf', width = 10, height = 10)
forest(caregiver_burden.m.Domain, subgroup.name = NULL, 
       prediction = TRUE, prediction.subgroup = TRUE)
dev.off()
```

### Meta-regression

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Year)
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg,
       studlab = TRUE, pos.studlab = 4,
       xlim = c(2008, 2022), ylim = c(-2.5, 1),
       xlab = "Covariate Year")
```
```{r}
caregiver_burden <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Caregiver_burden(Immediate)')
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 # subgroup = Caregiver.intervention.type,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~'Total_attrition.percent')
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg,
       studlab = TRUE, pos.studlab = 4,
       xlim = c(-1, 30), ylim = c(-2.5, 1),
       xlab = "Covariate attrition rate")
```

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Measurement.point)
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg,
       studlab = TRUE, pos.studlab = 4,
       xlim = c(0, 200), ylim = c(-2.5, 1),
       xlab = "Covariate Follow-up Duration (Days)")
```

```{r}
library(ggplot2)
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Treatment.duration)
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg, 
       studlab = TRUE, pos.studlab = 4,
       xlim = c(0, 200), ylim = c(-2.5, 1),
       xlab = "Covariate Treatment Duration (Days)")
```

```{r}
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 subgroup = Country,
                 # byvar = Effect.measure,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Caregiver.intervention.type)
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg)
```

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~as.factor(Caregiver.intervention.type))
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg,
       studlab = TRUE, pos.studlab = 4,
       xlim = c(0, 200), ylim = c(-2.5, 1),
       xlab = "Covariate risk of bias")
```






```{r}


caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Measurement.point)
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Treatment.duration)
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~Measurement.point * Treatment.duration)
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~as.factor(Caregiver.intervention.type))
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~as.factor(Caregiver.intervention.type) * Treatment.duration)
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~as.factor(Caregiver.intervention.type) * Measurement.point)
print(caregiver_burden.metareg)

caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Updated.Dementia.Severity)
print(caregiver_burden.metareg)

```

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~as.factor(Caregiver.intervention.type) * 
                                      Measurement.point *
                                      Country)
print(caregiver_burden.metareg)
```

## Caregiver QoL

```{r}
library(meta)
caregiver_QoL <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver quality of life',]
pdf('Figures/Caregiver_QoL_forest.pdf', width = 12, height = 3.2)
caregiver_QoL.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_QoL,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
forest(caregiver_QoL.m, prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
```

```{r}
library(metafor)
res <- rma(mean.effect, variance, data=caregiver_QoL, slab = Study.Identifier)
res <- rma(mean.effect, variance, 
           data=caregiver_QoL, 
           slab = Study.Identifier)
qqnorm(res)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
caregiver_QoL
```

## Caregiver depression

```{r}
library(meta)
caregiver_depression <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver depression',]
# caregiver_QoL <- caregiver_QoL[-5, ]
pdf('Figures/Caregiver_depression_forest.pdf', width = 12, height = 3.2)
caregiver_depression.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_depression,
                 sm = "SMD",
                 comb.fixed = TRUE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_depression.m
forest(caregiver_depression.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(caregiver_depression.m)
library(metafor)
res <- rma(mean.effect, variance, 
           data=caregiver_depression, 
           slab = Study.Identifier)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
```

### Caregiver anxiety

```{r}
library(meta)
caregiver_anxiety <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver anxiety',]
# caregiver_QoL <- caregiver_QoL[-5, ]
pdf('Figures/Caregiver_anxiety_forest.pdf', width = 12, height = 3.2)
caregiver_anxiety.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_anxiety,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_anxiety.m
forest(caregiver_anxiety.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(caregiver_anxiety.m)
library(metafor)
res <- rma(mean.effect, variance, 
           data=caregiver_depression, 
           slab = Study.Identifier)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
```

## Patient cognitive function

```{r}
patient_cognition <- read.xlsx('Dataset_effect_size_calculated_v1.xlsx', 
                               sheet = 'Patient cognitive function')
pdf('Figures/Patient_cognitive_function_forest.pdf', width = 12, height = 3.2)
patient_cognition.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = patient_cognition,
                 sm = "SMD",
                 comb.fixed = TRUE,
                 comb.random = FALSE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
forest(patient_cognition.m, prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
```

```{r}
library(meta)
patient_QoL <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Patient quality of life',]
pdf('Figures/Patient_QoL_forest.pdf', width = 12, height = 3.2)
patient_QoL.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = patient_QoL,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
patient_QoL.m
forest(patient_QoL.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(patient_QoL.m)
library(metafor)
res <- rma(mean.effect, variance, 
           data=patient_QoL, 
           slab = Study.Identifier)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac

patient_QoL <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Patient quality of life',]
patient_QoL <- patient_QoL[-1, ]
pdf('Figures/Patient_QoL_forest.pdf', width = 12, height = 3.2)
patient_QoL.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = patient_QoL,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
patient_QoL.m
forest(patient_QoL.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(patient_QoL.m, )
library(metafor)
res <- rma(mean.effect, variance, 
           data=patient_QoL, 
           slab = Study.Identifier)
gosh(res)
#gosh_diac <- gosh.diagnostics(gosh(res))
#plot(gosh_diac, which = "cluster")
#plot(gosh_diac, which = "outlier")
#gosh_diac
```

## Combine studies

```{r}
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = TRUE)

caregiver_depression.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_depression,
                 sm = "SMD",
                 comb.fixed = TRUE)

forest(metabind(caregiver_burden.m, caregiver_depression.m), prediction = TRUE)
```

