---
title: "Meta-analysis"
output:
  word_document: 
    toc: true
    toc_depth: 5
  pdf_document:
    toc: true
    toc_depth: 5
    latex_engine: xelatex
---

```{r eval = FALSE}
library(openxlsx)
library(metafor)
library(esc)
library(dmetar)
library(metafor)
library(dplyr)
```

## Meta-analysis with R

```{r}
meta_df.es.g <- read.xlsx('~/Documents/Coding/HP407/Sensitivity Analysis/Dataset_effect_size_calculated.xlsx')
meta_df.es.g.old <- read.xlsx('~/Documents/Coding/HP407/Dataset_effect_size_calculated.xlsx')
# setdiff(meta_df.es.g, meta_df.es.g.old)
colnames(meta_df.es.g)
```


### Perform meta-analysis with 'meta'

```{r}
es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
selected_names <- es.freq_df[es.freq_df$Freq < 4, ]$Var1
selected_names <- selected_names[grepl('Caregiver', selected_names)]
selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]

library(meta)
m.gen <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = selection_df,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = FALSE,
                 byvar = Effect.measure,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')


pdf('Figures/SA_combined_forest_1.pdf', width = 10, height = 8.4)
forest(m.gen, 
       prediction.subgroup = FALSE, subgroup.name = NULL, 
       overall = FALSE, overall.hetstat = FALSE, 
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Risk of bias'),
       xlim = c(-5, 5))
dev.off()

es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
selected_names <- es.freq_df[es.freq_df$Freq < 4, ]$Var1
selected_names <- selected_names[grepl('Patient', selected_names)]
selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]

m.gen <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = selection_df,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = FALSE,
                 byvar = Effect.measure,
                 
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')


pdf('Figures/SA_combined_forest_2.pdf', width = 10, height = 3.2)
forest(m.gen, 
       prediction.subgroup = FALSE, 
       subgroup.name = NULL, 
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Risk of bias'),
       overall = FALSE, 
       overall.hetstat = FALSE, 
       xlim = c(-5, 5))
dev.off()
```

```{r}
es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
selected_names <- es.freq_df[es.freq_df$Freq > 0, ]$Var1
# selected_names <- selected_names[grepl('Caregiver', selected_names)]
selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]

# colnames(caregiver_es)
# caregiver_es_names
caregiver.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = selection_df,
                 sm = "SMD",
                 comb.fixed = TRUE,
                 byvar = Effect.measure)
pdf('Figures/SA_combined_forest.pdf', width = 10, height = 30)
forest(caregiver.m, prediction.subgroup = TRUE, 
       subgroup.name = NULL, 
       overall = FALSE, overall.hetstat = FALSE,
       leftcols = NULL, # c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall')
       leftlabs = NULL, #c('Study Identifier', 
                  #  expression(N[Control]), 
                  #  expression(N[Intervention]), 
                  #  'Risk of bias'),
       study.results = FALSE,
       test.subgroup = FALSE,
       xlim = c(-14, 14), print.tau2 = FALSE,
       text.common = 'Fixed-effects model',
       text.random = 'Random-effects model'
       )
dev.off()

pdf('Figures/SA_combined_forest_full.pdf', width = 15, height = 50)
forest(caregiver.m, prediction.subgroup = TRUE, 
       subgroup.name = NULL, 
       overall = TRUE, overall.hetstat = TRUE,
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    'Risk of bias'),
       study.results = TRUE,
       test.subgroup = TRUE,
       xlim = c(-14, 14), print.tau2 = TRUE,
       text.common = 'Fixed-effects model',
       text.random = 'Random-effects model'
       )
dev.off()
```

### Caregiver burden

#### Perform meta-analysis with 'metafor'

```{r eval = FALSE}
library(metafor)
caregiver_burden <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver burden',]
# caregiver_burden
res <- rma(mean.effect, variance, data=caregiver_burden, slab = Study.Identifier)
# res
# forest(res)
```

#### Perform GOSH analysis with 'metafor'

```{r eval = FALSE}
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
```

#### GOSH after removing outliers

```{r eval = FALSE}
res <- rma(mean.effect, variance, 
           data=caregiver_burden[-1, ], 
           slab = Study.Identifier)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
```

#### Perform meta-analysis with 'meta'

```{r}
colnames(caregiver_burden)
```

```{r}
#es.freq_df <- data.frame(table(meta_df.es.g$Effect.measure))
#selected_names <- es.freq_df[es.freq_df$Freq < 4, ]$Var1
#selected_names <- selected_names[grepl('Patient', selected_names)]
#selection_df <- meta_df.es.g[meta_df.es.g$Effect.measure %in% selected_names, ]
caregiver_burden <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver burden',]

caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 # byvar = Effect.measure,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')

pdf('Figures/SA_caregiver_burden_forest_with_outlier.pdf', width = 10, height = 5)
forest(caregiver_burden.m, 
       prediction = TRUE,
       prediction.subgroup = TRUE, 
       sortvar = Year,
       subgroup.name = NULL, 
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()

caregiver_burden <- caregiver_burden[
  -which(caregiver_burden$Study.Identifier == 'Govindakumari 2020'), 
  ]
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 # byvar = Effect.measure,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')

pdf('Figures/SA_caregiver_burden_forest_without_outlier.pdf', width = 10, height = 5)
forest(caregiver_burden.m, 
       predict = TRUE,
       prediction.subgroup = TRUE, 
       sortvar = Year,
       subgroup.name = NULL, 
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")),
       overall = TRUE, 
       overall.hetstat = TRUE, 
       xlim = c(-7, 7))
dev.off()
```

#### Funnel plot

```{r eval = FALSE}
pdf('Figures/SA_SA_caregiver_burden_funnel.pdf', width = 10, height = 7)
# funnel(m.gen, studlab = TRUE, xlim = c(-8, 1))
col.contour = c("gray75", "gray85", "gray95")
funnel.meta(m.gen, xlim = c(-6.2, 1.2),
            contour = c(0.9, 0.95, 0.99),
            col.contour = col.contour, 
            studlab = TRUE, pos.studlab = '4')

# Add a legend
legend(x = -4, y = 0.01, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)
dev.off()
```

#### Subgroup analysis by country

```{r eval = FALSE}
caregiver_burden.m.by.country <- update.meta(caregiver_burden.m, 
            subgroup = Country, 
            tau.common = FALSE)
pdf('Figures/SA_caregiver_burden_country.pdf', width = 10, height = 7.5)
forest(caregiver_burden.m.by.country, 
       subgroup.name = NULL, 
       prediction = TRUE, 
       prediction.subgroup = FALSE,
       leftcols = c('Study.Identifier','Ctrl_Post_N', 'Expt_Post_N',  'Overall'),
       leftlabs = c('Study Identifier', 
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")),
       )
dev.off()
caregiver_burden.m.by.country
```

```{r}
caregiver_burden.m.by.country
```

#### Subgroup analysis by intervention type

```{r eval = FALSE}
caregiver_burden.m.by.intervention <- update.meta(caregiver_burden.m, 
            subgroup = Caregiver.intervention.type, tau.common = FALSE)
caregiver_burden.m.by.intervention
pdf('Figures/SA_caregiver_burden_intervention.pdf', width = 10, height = 10)
forest(caregiver_burden.m.by.intervention, subgroup.name = NULL, 
       prediction = TRUE, prediction.subgroup = TRUE)
dev.off()
```

```{r}
caregiver_burden.m.Domain <- update.meta(caregiver_burden.m, 
            subgroup = Domain.1.unmodified, tau.common = FALSE)
caregiver_burden.m.Domain
pdf('Figures/SA_caregiver_burden.m.Domain.pdf', width = 10, height = 10)
forest(caregiver_burden.m.Domain, subgroup.name = NULL, 
       prediction = TRUE, prediction.subgroup = TRUE)
dev.off()
```

### Meta-regression

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Year)
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg)
```

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Measurement.point)
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg, studlab = TRUE, xlab = "Covariate Measurement Duration (Days)")
```

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Treatment.duration)
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg, studlab = TRUE, xlim = c(0, 200), ylim = c(-2.5, 1),
       xlab = "Covariate Treatment Duration (Days)")
```

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Caregiver.intervention.type)
print(caregiver_burden.metareg)
bubble(caregiver_burden.metareg)
```

```{r}


caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Measurement.point)
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Treatment.duration)
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~Measurement.point * Treatment.duration)
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~as.factor(Caregiver.intervention.type))
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~as.factor(Caregiver.intervention.type) * Treatment.duration)
print(caregiver_burden.metareg)
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~as.factor(Caregiver.intervention.type) * Measurement.point)
print(caregiver_burden.metareg)

caregiver_burden.metareg <- metareg(caregiver_burden.m, ~Updated.Dementia.Severity)
print(caregiver_burden.metareg)

```

```{r}
caregiver_burden.metareg <- metareg(caregiver_burden.m, 
                                    ~as.factor(Caregiver.intervention.type) * 
                                      Measurement.point *
                                      Country)
print(caregiver_burden.metareg)
```

## Caregiver QoL

```{r}
library(meta)
caregiver_QoL <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver quality of life',]
pdf('Figures/SA_Caregiver_QoL_forest.pdf', width = 12, height = 3.2)
caregiver_QoL.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_QoL,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
forest(caregiver_QoL.m, prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
```

```{r}
library(metafor)
res <- rma(mean.effect, variance, data=caregiver_QoL, slab = Study.Identifier)
res <- rma(mean.effect, variance, 
           data=caregiver_QoL[-1, ], 
           slab = Study.Identifier)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
caregiver_QoL
```

```{r}
library(meta)
caregiver_QoL <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver quality of life',]
caregiver_QoL <- caregiver_QoL[-5, ]
pdf('Figures/SA_Caregiver_QoL_forest_without_outlier.pdf', width = 12, height = 3.2)
caregiver_QoL.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_QoL,
                 sm = "SMD",
                 comb.fixed = TRUE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_QoL.m
forest(caregiver_QoL.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(caregiver_QoL.m)
library(metafor)
res <- rma(mean.effect, variance, data=caregiver_QoL, slab = Study.Identifier)
res <- rma(mean.effect, variance, 
           data=caregiver_QoL, 
           slab = Study.Identifier)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
caregiver_QoL[4,]
```

## Caregiver depression

```{r}
library(meta)
caregiver_depression <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver depression',]
# caregiver_QoL <- caregiver_QoL[-5, ]
pdf('Figures/SA_Caregiver_depression_forest.pdf', width = 12, height = 3.2)
caregiver_depression.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_depression,
                 sm = "SMD",
                 comb.fixed = TRUE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_depression.m
forest(caregiver_depression.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(caregiver_depression.m)
library(metafor)
res <- rma(mean.effect, variance, 
           data=caregiver_depression, 
           slab = Study.Identifier)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
```

## Caregiver anxiety

```{r}
library(meta)
caregiver_anxiety <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Caregiver anxiety',]
# caregiver_QoL <- caregiver_QoL[-5, ]
pdf('Figures/SA_Caregiver_anxiety_forest.pdf', width = 12, height = 3.2)
caregiver_anxiety.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_anxiety,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
caregiver_anxiety.m
forest(caregiver_anxiety.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(caregiver_anxiety.m)
library(metafor)
res <- rma(mean.effect, variance, 
           data=caregiver_depression, 
           slab = Study.Identifier)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac
```

## Patient cognitive function

```{r}
patient_cognition <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Patient cognitive function',]
pdf('Figures/SA_Patient_cognitive_function_forest.pdf', width = 12, height = 3.2)
patient_cognition.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = patient_cognition,
                 sm = "SMD",
                 comb.fixed = TRUE,
                 comb.random = FALSE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
forest(patient_cognition.m, prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
```

```{r}
library(meta)
patient_QoL <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Patient quality of life',]
pdf('Figures/SA_Patient_QoL_forest.pdf', width = 12, height = 3.2)
patient_QoL.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = patient_QoL,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
patient_QoL.m
forest(patient_QoL.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(patient_QoL.m)
library(metafor)
res <- rma(mean.effect, variance, 
           data=patient_QoL, 
           slab = Study.Identifier)
library(dmetar)
gosh_diac <- gosh.diagnostics(gosh(res))
plot(gosh_diac, which = "cluster")
plot(gosh_diac, which = "outlier")
gosh_diac

patient_QoL <- meta_df.es.g[meta_df.es.g$Effect.measure == 'Patient quality of life',]
patient_QoL <- patient_QoL[-1, ]
pdf('Figures/SA_Patient_QoL_forest.pdf', width = 12, height = 3.2)
patient_QoL.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = patient_QoL,
                 sm = "SMD",
                 comb.fixed = FALSE,
                 comb.random = TRUE,
                 text.common = 'Fixed-effects model',
                 text.random = 'Random-effects model')
patient_QoL.m
forest(patient_QoL.m, 
       prediction = TRUE, 
       leftcols = c('Study.Identifier',
                    'Caregiver.intervention.subgroups',
                    'Ctrl_Post_N', 
                    'Expt_Post_N',  
                    'Overall'),
       leftlabs = c('Study Identifier', 
                    'Intervention content',
                    expression(N[Control]), 
                    expression(N[Intervention]), 
                    expression("Overall risk of bias")))
dev.off()
funnel(patient_QoL.m, )
library(metafor)
res <- rma(mean.effect, variance, 
           data=patient_QoL, 
           slab = Study.Identifier)
gosh(res)
#gosh_diac <- gosh.diagnostics(gosh(res))
#plot(gosh_diac, which = "cluster")
#plot(gosh_diac, which = "outlier")
#gosh_diac
```

## Combine studies

```{r}
caregiver_burden.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_burden,
                 sm = "SMD",
                 comb.fixed = TRUE)

caregiver_depression.m <- metagen(TE = mean.effect,
                 seTE = standard_error,
                 studlab = Study.Identifier,
                 data = caregiver_depression,
                 sm = "SMD",
                 comb.fixed = TRUE)

forest(metabind(caregiver_burden.m, caregiver_depression.m), prediction = TRUE)
```

