Source: https://stat.ethz.ch/pipermail/r-help/2015-April/427661.html

This is my dataset (with imputed r = 0.70 for pre-post correlation, put in
the 'ri' variable):

##### the data

```{r}
dat <- structure(list(study = structure(c(11L, 8L, 7L, 12L, 13L, 4L,
5L, 1L, 10L, 3L, 6L, 9L, 2L), .Label = c("Study A, 2012",
"Study B, 2013", "Study C, 2013", "Study D, 2010",
"Study E, 2012", "Study F, 2013", "Study G, 2006",
"Study H, 2005", "Study I, 2013", "Study L, 2012",
"Study M, 2003", "Study N, 2007", "Study P, 2007"
), class = "factor"), c_pre_mean = c(4.9, 15.18, 19.01, 5.1,
16.5, 27.35, 18.1, 2.4, 14.23, 0.08, 21.26, 21.5, 21.73), c_pre_sd = c(2.6,
2.21, 7.1, 1.5, 7.2, 13.92, 5.4, 0.13, 4.89, 0.94, 7.65, 5.22,
8.43), c_post_mean = c(6.1, 13.98, 18.5, 4.53, 15.9, 23, 16.9,
2.2, 16.58, -0.02, 16, 16.84, 23.54), c_post_sd = c(2.06, 3.24,
7, 2.06, 6.8, 12.06, 3.8, 0.13, 6.35, 0.88, 4.69, 4.64, 6.74),
    c_sample = c(14, 13, 19, 15, 34, 20, 24, 35, 31, 26, 49,
    21, 22), e_pre_mean = c(4.6, 13.81, 19.9, 5.3, 18.7, 22.71,
    19.2, 2.7, 15.97, -0.22, 20.9, 20.43, 21.94), e_pre_sd = c(2.1,
    6.64, 8.1, 2.9, 7.3, 7.82, 4.1, 0.13, 6.73, 0.93, 5.18, 4.87,
    7.02), e_post_mean = c(4.64, 15.86, 18.1, 4.33, 17.2, 24.89,
    17.6, 2.8, 13.6, 0.06, 17.41, 16.05, 19.29), e_post_sd = c(2.34,
    7.76, 7.8, 2.26, 7.4, 11.89, 3.7, 0.13, 5.79, 1.12, 5.16,
    4.17, 6.58), e_sample = c(14, 18, 16, 16, 33, 28, 29, 36,
    38, 27, 43, 25, 17), ri = c(.70,
.70,.70,.70,.70,.70,.70,.70,.70,.70,.70,.70,.70)), .Names = c("study",
"c_pre_mean", "c_pre_sd",
"c_post_mean", "c_post_sd", "c_sample", "e_pre_mean", "e_pre_sd",
"e_post_mean", "e_post_sd", "e_sample", "ri"), class = "data.frame",
row.names = c(NA,
-13L))

### check the data

dim(dat)
head(dat)
str(dat)

```

attach(dat) #### yes, I know, do'nt do this....

# call the library
```{r}
library(metafor)
```

# Computing Standardized Mean Difference (Hedges' g) for Each Group
(experimental and control) at post treatment
# use "SMD" for the standardized mean difference using raw score
standardization

```{r}
datT <- escalc(measure="SMD", m1i=e_post_mean, sd1i=e_post_sd,
n1i=e_sample, m2i=c_post_mean, sd2i=c_post_sd, n2i=c_sample, vtype="UB",
data=dat, append=TRUE)
```

# Extract the effect size ( Standardized Mean Difference (Hedges' g)) and
its variance

```{r}
yi <- datT$yi
yi
vi <- datT$vi
vi
```


###############################################
#
# fixed-effects model
#
###############################################

```{r}
model.FE <- rma(yi, vi, method="FE", digits=2)
summary(model.FE)
```


# plot globale

```{r}
plot(model.FE)
```
